Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-11-16 paper/ms.tex
Working on the Brooks et al hybrid model manuscript.

\begin{abstract}
Type Ia Supernovae are thermonuclear explosions of white dwarf (WD) stars.
Past studies predict the existence of "hybrid" white dwarfs, made of a C/O/Ne
core with a O/Ne shell, and that these are viable progenitors for supernovae.
More recent work found that the C/O core is mixed with the surrounding O/Ne
while the WD cools. Inspired by this scenario, we performed simulations of
thermonuclear supernovae in the single degenerate paradigm from these hybrid
progenitors. A hybrid white dwarf model constructed with the one-dimensional
stellar evolution code MESA[5] was provided (Brooks et al. 2017) for our
simulations.  This model had been run through the phase of unstable interior
mixing followed by accretion until central ignition of carbon burning. The
MESA model was then mapped to a two-dimensional initial condition and an
explosion simulated from that with FLASH[4]. For comparison, a similar
simulation of an explosion was performed from a traditional C/O progenitor
WD. Comparing the yields produced by explosion simulations allows us to
determine which model produces more 56Ni, and therefore brighter events, and
how explosions from these models differ from explosions from previous models
without the mixing during the WD cooling.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Type Ia supernovae (\SNeIa) are bright stellar explosions....

@@

Phillips relation
~\citep{phillips:absolute}.

Cosmology
due to dark energy \citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}.

@@

@@

Here's the other Books paper \citep{brookset2017}. Do we need to mention it?
Give a read to see!

>>>>

\begin{abstract}
Recent studies of stellar evolution predict the existence of "hybrid" white 
dwarfs, made of a C/O/Ne
core within a O/Ne shell, and that these are viable progenitors for supernovae.
More recent work found that the C/O core is mixed with the surrounding O/Ne
while the WD cools. Inspired by this scenario, we performed simulations of
thermonuclear supernovae from these hybrid progenitors. The progenitor model 
was constructed with the one-dimensional stellar evolution code MESA and
represented a star evolved through the phase of unstable interior mixing 
followed by accretion until it reached conditions for the ignition of 
carbon burning. The MESA model was then mapped to a two-dimensional initial 
condition and an explosion simulated with FLASH. For comparison, a similar
simulation of an explosion was performed from a traditional C/O progenitor
WD. By comparing the yields of the explosions, we found....
how explosions from these models differ from explosions from previous models
without the mixing during the WD cooling.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
thought to occur when approximately 1.5 \Msun of material composed principally 
of C and O burns under degenerate conditions. This class of supernovae is
know to synthesize much of the Fe-group elements found in the galaxy and
the light curves of these events have a spectial property that allows
their use as distance indicators for cosmological studies~\citep{phillips:absolute}
resulting in the discovery of the acceleration of the expansion of
the Universe and thus the inference of Dark 
Energy~\citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}.

Supernovae are observationally classified 
by their light curves and spectra~~\citet{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios, the {\em double detonation} or {\em sub-Chandrasekhar}
scenario, the {\em white dwarf merger} scenario, and  
the {\em single degenerate} scenario.

@@

@@

\citet{woosleyweavertaam80,taam80a,taam80b, nomoto80,nomoto82b} subchandra

@@

Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
Give a read to see!
